---
title: "Trucker Experiment monitoring"
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 3
    number_sections: yes
    theme: lumen
resource_files:
- crops_id.csv
---

```{r setup, include=FALSE}
# set up
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message = F)
options(scipen=5)


```


```{r read data, include = FALSE, echo=FALSE}

# survey data
# villages
mnt <- read.csv(file.path(output, "mnt_upd.csv"))
# crops
crops <- read.csv(file.path(output, "crops_upd.csv"))
# truckers
truc <- read.csv(file.path(input, "Trucker monitoring-survey-trucker.csv"))

```


# Monitoring Villages 
```{r summary, echo=FALSE}
# summary
st <- mnt %>% ungroup() %>% 
  summarise(villages=n_distinct(village_id),
                        villages_trucker_show=sum(trucker_present,na.rm = T),
                        per_aggregator_trans=100*sum(aggregator_transp,na.rm=T)/villages)

st %>%
  kable(booktabs = TRUE,
        col.names = c('No.Villages','Villages where trucker show up',
                      '%Villages where aggregator transported')) %>%
  kable_styling(bootstrap_options = "condensed",
                font_size = 14, full_width = FALSE, position = "left")


```


Villages by monitoring type 

```{r table 1, echo=FALSE}
mnt %>% group_by(monitoring_type) %>% 
  summarise(villages=n()) %>%
  mutate(per_villages=round(villages*100/sum(villages),2)) %>% 
  mutate(monitoring_type=ifelse(monitoring_type==1,'Enumerator is present','Phone call with village leader')) %>% 
  kable(booktabs = TRUE) %>%
  kable_styling(bootstrap_options = "condensed",
                font_size = 14, full_width = FALSE, position = "left")

```



```{r plot 1, echo=FALSE}
# plot number of truckers in village 
ggplot(mnt) + 
  geom_bar(aes(x = factor(num_truckers), y = ..count..,group=1),
           stat = "count",fill="darkblue")+
  labs(title='Number of truckers in village',y='Villages',x='Number of truckers')
  

```

```{r plot 2, echo=FALSE}
# plot number of farmers in village 
ggplot(mnt, aes(x=number_farmers))+
  geom_histogram(fill="darkblue")+ 
  labs(title='Number of farmers',x='Number of farmers',
       y='Villages')+
  scale_x_continuous(breaks = seq(0,7, by = 1))

# table number of farmers per village 
mnt %>% group_by(village_id) %>% 
  select(district, market,number_farmers) %>%  
  kable(booktabs = TRUE) %>%
  kable_styling(bootstrap_options = "condensed",
                font_size = 14, full_width = FALSE, position = "left")
```

Did the trucker transport crops from other farmers along the way?
```{r other transport, echo=FALSE}

mnt %>% group_by(other_transp) %>% 
  summarise(villages=n()) %>%
  mutate(per_villages=round(villages*100/sum(villages),2)) %>% 
  mutate(other_transp=ifelse(other_transp==1,'Yes','No')) %>% 
  kable(booktabs = TRUE) %>%
  kable_styling(bootstrap_options = "condensed",
                font_size = 14, full_width = FALSE, position = "left")

```

Aggregator transported crops with the trucker

```{r agg transport, echo=FALSE}

mnt %>% group_by(aggregator_transp) %>% 
  summarise(villages=n()) %>%
  mutate(per_villages=round(villages*100/sum(villages),2)) %>% 
  mutate(aggregator_transp=ifelse(aggregator_transp==1,'Yes','No')) %>% 
  kable(booktabs = TRUE) %>%
  kable_styling(bootstrap_options = "condensed",
                font_size = 14, full_width = FALSE, position = "left")

```


Villages where truckers show up

```{r Villages truckers, echo=FALSE}
mnt %>% mutate(trucker_showup=ifelse(trucker_present>0,"Yes","No")) %>% 
  group_by(trucker_showup) %>% summarise(num_villages=n()) %>% 
  mutate(per_vill=100*num_villages/sum(num_villages)) %>%  
  kable(booktabs = TRUE) %>%
  kable_styling(bootstrap_options = "condensed",
                font_size = 14, full_width = FALSE, position = "left")



```
Did the trucker use the sampled feeder road to reach the market & village?
```{r sampled road, echo=FALSE}
ggplot(mnt) + 
  geom_bar(aes(x = factor(sampled_road_taken), y = ..prop..,group=1),
           stat = "count",fill="darkblue")+
  scale_y_continuous(labels = scales::percent_format())+
  labs(title='Sampled road taken',y='%',x='')+
  scale_x_discrete(labels=c("1" = "Yes","0"="No","NA"="NA"))
```


Is the road from the village to the market rehabilitated?
```{r road rehabilitated, echo=FALSE}
mnt %>% mutate(road_rehab=ifelse(road_rehab=='1','Yes',ifelse(road_rehab==0,'No',NA))) %>% 
  ggplot() + 
  geom_bar(aes(x = factor(road_rehab), y = ..prop..,group=1),
           stat = "count",fill="darkblue")+
  scale_y_continuous(labels = scales::percent_format())+
  labs(title='Road rehabilitated',y='%',x='')
```


What is the road condition from the village to the market? 
```{r road condition, echo=FALSE}
mylabels <- c('Very bad','Bad','Fairly good','Very good',NA)
ggplot(mnt) + 
  geom_bar(aes(x = factor(road_condition_new), y = ..prop..,group=1),
           stat = "count",fill="darkblue")+
  scale_y_continuous(labels = scales::percent_format())+
  labs(title='Road condition',y='%',x='')+
  scale_x_discrete(labels=mylabels)

```

# Monitoring crops

```{r plot 3, echo=FALSE}

crops %>% 
  ggplot(aes(x=name_eng)) + 
  geom_bar(aes(y = ..prop.., group = 1),fill="darkblue")+
  labs(title='Crops transported',y='%',x='Crop')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_y_continuous(labels = scales::percent_format())
```

Total quantities transported in Kg
```{r quantities, echo=FALSE}
crops %>% group_by(name_eng) %>% 
  summarise(quant_farmers_total=sum(quant_crops_farmers,na.rm=T),
            quant_agreggator_total=sum(quant_crops_aggregator,na.rm=T)) %>%  
  kable(booktabs = TRUE) %>%
  kable_styling(bootstrap_options = "condensed",
                font_size = 14, full_width = FALSE, position = "left")



```

# Monitoring truckers
Contract awarded during the WTA
```{r contracts truckers, echo=FALSE}

truc %>% 
  ggplot(aes(x=factor(contract_wta))) + 
  geom_bar(aes(y = ..prop.., group = 1),fill="darkblue")+
  labs(title='Contract wta',y='%',x='')+
  scale_y_continuous(labels = scales::percent_format())+
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes"))
```